\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\usepackage{charter}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.65in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands for resume items
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}
\vspace*{10pt} % Add some space at the top

%----------HEADING----------
\begin{center}
    {\Huge \scshape \textbf{Mohd Amaan}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height} ~ \href{mailto:amaanrizvi73@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  {amaanrizvi73@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/amaan8429}{\raisebox{-0.2\height}\faLinkedin\ {LinkedIn}} ~
    \href{https://github.com/amaan8429}{\raisebox{-0.2\height}\faGithub\ {GitHub}} ~
    \href{https://amaan.zip}{\raisebox{-0.2\height}\faGlobe\ {amaan.zip}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \item
      \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{Dr. A. P. J. Abdul Kalam Technical University} & \textbf{\small Expected May 2026} \\
        \textit{\small Bachelor of Technology in Computer Science} & \textit{\small Lucknow, India} \\
      \end{tabular*}

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

        \resumeProjectHeading
          {\textbf{Cur8t} $|$ \emph{Next.js, TypeScript, ShadcnUI, AI, Neon, Drizzle}}{{\href{https://cur8t.com/}{\faGlobe\ Live} \href{https://github.com/amaan8429/cur8t}{\faGithub\ GitHub} \href{https://x.com/amaan8429/status/1960596953479438587}{\faVideo\ Video}}}
          \resumeItemListStart
            \resumeItem{AI-powered bookmark manager with smart organization, browser extension, and GitHub sync integration.}
            \resumeItem{Features collections management (public/private/protected), article link extraction, and collaboration tools.}
            \resumeItem{Built with microservices architecture using Docker, Redis caching, and comprehensive export options.}
          \resumeItemListEnd
          \vspace{-13pt}

        \resumeProjectHeading
          {\textbf{Rotreels} $|$ \emph{Next.js, TypeScript, ShadcnUI, AI, PostgreSQL, FFmpeg}}{{\href{https://rotreels.com/}{\faGlobe\ Live} \href{https://github.com/amaan8429/rotreels}{\faGithub\ GitHub}}}
          \resumeItemListStart
            \resumeItem{AI-powered video creation platform for viral content with character voices, voice cloning, dynamic backgrounds.}
            \resumeItem{Implements multi-voice system with ElevenLabs integration, Whisper for transcription, and AWS S3 storage.}
            \resumeItem{Features conversational AI, real-time progress tracking, and professional video rendering with subtitle system.}
          \resumeItemListEnd
          \vspace{-13pt}

        \resumeProjectHeading
          {\textbf{Emotion Prompt} $|$ \emph{Next.js, TypeScript, ShadcnUI, OpenAI API, PWA}}{{\href{https://emotionpromptingis.art}{\faGlobe\ Live} \href{https://github.com/amaan8429/emotion-prompt}{\faGithub\ GitHub}}}
          \resumeItemListStart
            \resumeItem{Enhance AI prompts with psychological stimuli based on research proven to improve LLM performance.}
            \resumeItem{Features psychological stimuli integration, research-based optimization, and real-time prompt improvement.}
            \resumeItem{Built with beautiful responsive UI, PWA support, offline capabilities, and scientific data visualizations.}
          \resumeItemListEnd
          \vspace{-13pt}

        \resumeProjectHeading
          {\textbf{Next Clean} $|$ \emph{TypeScript}}{{\href{https://www.npmjs.com/package/next-clean}{\faGlobe\ Live} \href{https://github.com/amaan8429/next-clean}{\faGithub\ GitHub}}}
          \resumeItemListStart
            \resumeItem{A clean Next.js template without the boilerplate code. Type-safe and easy to use.}
          \resumeItemListEnd
    
    \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {B2B Stealth}{Jan 2025 -- Present}
      {Full Stack Developer}{}
      \resumeItemListStart
        \resumeItem{Building a B2B SaaS platform for a US-based startup, collaborating with a team of talented individuals.}
        \resumeItem{Worked in Firebase and FastAPI backend while developing the entire Flutter frontend from scratch.}
        \resumeItem{Optimized the product using various caching and database indexing techniques.}
      \resumeItemListEnd

    \resumeSubheading
      {Ayka India Trust}{April 2024 -- June 2024}
      {Backend Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Implemented SMTP, volunteer registration systems, and integrations to streamline workflows.}
        \resumeItem{Assisted in building their volunteer database management system.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages:} TypeScript, JavaScript, Python, Dart, Solidity, Go \\
    \textbf{Frontend:} Next.js, React.js, Flutter, Tailwind CSS, ShadcnUI, Framer Motion, Radix UI \\
    \textbf{Backend \& AI:} FastAPI, NestJS, OpenAI API, ElevenLabs, Whisper, FFmpeg, Remotion \\
    \textbf{Databases:} PostgreSQL, MongoDB, Redis, Neon, Drizzle, Prisma \\
    \textbf{DevOps:} Docker, Nginx, Vercel, AWS S3, BullMQ, Zustand, React Query \\
    \textbf{Developer Tools:} Postman, PostHog, Upstash, Firebase, Supabase, Hardhat, Clerk
  }}
\end{itemize}
\vspace{-16pt}

\section{Certifications \& Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Certifications:} NYU Startup Accelerator Program \\[3pt]
      \textbf{Leadership:} Organizer of college-level hackathons and college events.\\[3pt]
      \textbf{Content Creation:} Tech content creator with viral Twitter videos and IG Reels. \\[3pt]
    }}
 \end{itemize}


\end{document}